### 2018-04-15 manuscript.Rnw
intro bullet point a first part2

The significANCE AND determinism OF ANIMAL BEHAVIOUR has long been quiestion of prime interest.
In the 1960s researchers started to identify genetic determinant of behaviours.
OUr ability to understand genetics has been enpowered by new high throuput methods.
The scoring of behaviour as well is undergoing a transition towards high througput (ethomics, CE).

>>>>

The significANCE AND determinism OF ANIMAL BEHAVIOUR has long been question of prime interest.
In the 1960-70s genetics and behaviour inerpenetrated as researchers started to identify genetic determinant of behaviours.
OUr ability to understand genetics and neurobiology has been enpowered by new high throughput methods and data analysis.
The scoring of behaviour as well is undergoing a transition towards high througput (ethomics, CE).
